Paper Figure Generation

### 2022-12-02 R/PaperFigureGeneration.rmd
Added new figure (now S5) for 3' nuc freq.

```{r read_figure_S5_data}
NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "GG>AA",
    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
  ))
}

@@

```{r figure_S5, fig.width = 5, fig.height = 5.5}
plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative GG>AA Frequency")
```

>>>>

```{r read_figure_S5_data}
NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered = fread(generateFilePath(
  NHF1ExcisionSiteDataDirectory, dataTypeStrings$nucleotideFrequencyData, ".tsv",
  cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
  strandPolarity = "five_prime", anchored = TRUE, filtering = "TGG_filtered"
))
```

```{r figure_S5, fig.width = 6.5, fig.height = 6}
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = THREE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 6, maxReadLength = 12,
                               xAxisLabel = "Mismatch Relative Position")
```

```{r read_figure_S6_data}
NHF1CPDGGtoAAMismatchDataAllRepsFiltered = NHF1CPDTimepoints
for (i in seq_along(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)) {
  NHF1CPDGGtoAAMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    NHF1SequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "NHF1", lesion = "CPD", repitition = "all_reps",
    filtering = "TGG_filtered", includedMismatches = "GG>AA",
    timepoint = names(NHF1CPDGGtoAAMismatchDataAllRepsFiltered)[i]
  ))
}

@@

```{r figure_S6, fig.width = 5, fig.height = 5.5}
plotPositionAcrossTimepointAndReadLength(NHF1CPDGGtoAAMismatchDataAllRepsFiltered["1h"],
                                         title = "NHF1 CPD All Reps GG>AA Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDGGtoAAMMFreqZScoresAllRepsFiltered,
                                         yAxisLabel = "Relative GG>AA Frequency")
```
